Homework Report

### 2017-02-15 work/work.tex
Changing heuristic C to D and adding new heuristic C

@@

@@

>>>>

\heuristic{}\label{heuristic-dsatur}

Heuristic \ref{heuristic-dsatur} is very similar to heuristic \ref{heuristic-welsh}, but colors based on the \emph{saturation} degree of vertices, which is defined below by \cite{spinrad}. The original DSATUR algorithm was proposed by \cite{brelaz}.

\begin{definition}[Saturation degree]
The saturation degree of a vertex is the number of different colors used for vertices adjacency to it.
\end{definition}

\begin{algorithm}
\caption{DSATUR algorithm}
\begin{algorithmic}[1]
\State Find the vertex $\in V$ with maximum degree and color it with color 1
\While{There are uncolored vertices}
\State Choose an uncolored vertex with maximum saturation degree
\State If there is a tie, choose the vertex with maximum degree
\State Color the vertex with the least possible number
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\bibitem{brelaz}
Brélaz, D. [1979]. \emph{New methods to color the vertices of a graph}. Communications of the ACM, 22(4), pp.251-256.

@@

\bibitem{spinrad}
Spinrad, J. P. and Vijayan, G. [1985], \emph{Worst case analysis of a graph coloring algorithm}. Discrete Applied Mathematics, 12(1), pp.89-92.
